---
title: "shinyLabView docs"
output:
  html_document:
    df_print: paged
---

(assorted write-along during programming)

# What?
This is a Shiny web app to visualize lab results from csv input data.
This is a study-project from "Beuth University of Apllied Sciences (https://www.beuth-hochschule.de)

Students: 
* Semra Kocack
* Christopher Secker
* Markus Bockhacker

Currently this project has no licence - this will change in the future.


# CAVE / BEWARE:
this projects uses lab parameters that are familiar to german physicians in clinical practice and therefore are not always proper si-units!

### Lab Data (input)
comma-separated-values (csv) are read from a file.

```{r echo=FALSE, results='asis'}
library(knitr)
kable(read.csv("./input_data_structures/lab-Lab results input data structure.csv", header = TRUE, sep = ";"))
```

### Lookup table for patient-data
comma-separated-values (csv) are read from a file.

```{r echo=FALSE, results='asis'}
library(knitr)
kable(read.csv("./input_data_structures/patient_lookup-patient data lookup table structure sheet.csv", header = TRUE, sep = ";"))
```

### Normal values
comma-separated-values (csv) are read from a file.

```{r echo=FALSE, results='asis'}
library(knitr)
kable(read.csv("./input_data_structures/norm-Lab results input data structure.csv", header = TRUE, sep = ";"))
```
