---
title: "shinyLabView docs"
output:
  html_document:
    df_print: paged
---

(assorted write-along during programming)

# What?
This is a Shiny web app to visualize lab results from csv input data.
This is a study-project from "Beuth University of Apllied Sciences (https://www.beuth-hochschule.de)

Students: 
* Semra Kocack
* Christopher Secker
* Markus Bockhacker

Currently this project has no licence - this will change in the future.


## CAVE / BEWARE:
this projects uses lab parameters that are familiar to german physicians in clinical practice and therefore are not always proper si-units!

#### Lab Data (input)
comma-separated-values (csv) are read from a file.

```{r echo=FALSE, results='asis'}
library(knitr)
kable(read.csv2("./input_data_structures/lab-Lab results input data structure.csv"))
```

#### Lookup table for patient-data
comma-separated-values (csv) are read from a file.

```{r echo=FALSE, results='asis'}
library(knitr)
kable(read.csv2("./input_data_structures/patient_lookup-patient data lookup table structure sheet.csv"))
```

#### Normal values
comma-separated-values (csv) are read from a file.
Source: http://www.laborlexikon.de/Referenzen.htm

```{r echo=FALSE, results='asis'}
library(knitr)
kable(read.csv2("./input_data_structures/norm-Lab results input data structure.csv"))
```


### Random Datasets
```{r}
library(lubridate)
normvalues <- read.csv2("./input_data_structures/norm-Lab results input data structure.csv")

store <- list()
v <- numeric(14)
k <- 0

for (i in 1:40) {
  for (j in 1:20) {
    k <- k+1
    v[1] <- k # resultId
    v[2] <- j # patientId
    v[3] <- as_datetime(now() - runif(1, 0, 10^7)) # Unix Timestamp magic
    v[4] <- runif(1, 120.0, 155.0) # na
    v[5] <- runif(1, 2.0, 10.5) # k
    v[6] <- runif(1, 0.2, 10.0) # krea
    v[7] <- runif(1, 10.0, 80.0) # hst
    v[8] <- runif(1, 0, 250) # gfr
    v[9] <- runif(1, 2.0, 18.0) # hgb
    v[10] <- runif(1, 2.0, 6.0) # rbc
    v[11] <- runif(1, 4000, 2*10^6) # plt
    v[12] <- runif(1, 100, 40000) # wbc
    v[13] <- runif(1, 0.1, 5.0) # inr
    v[14] <- runif(1, 15, 80) # ptt
    
    store[[k]] <- v
  }
}

store <- as.data.frame(do.call("rbind", store))
colnames(store) <- c("resultId", "patientId", "date", "na", "k", "krea", "hst", "gfr", "hgb", "rbc", "plt", "wbc", "inr", "ptt") 

write.csv2(store, "./dummyValues.csv")
```

## "internal API"
In order to build a modular program there's need for an internal api or convention on how to call testcases.
Testcases can either reverence the whole dataset or a subset by patientId and/or date.

Pseudocode:

    function testCase1 (dataSet, patientId, timeStampFrom, timeStampTo) {
      ...
      return MessageString "result"
    }
